\boldmath Disconnected pseudo-$C_\ell$ covariances for projected large-scale structure data

### 2019-06-24 draft/paper.tex
2.3. Cov mat: commas, etc

      Let $A$ and $F$ be the vector indices corresponding to the pairs of field indices $(\alpha,\beta)$ and $(\phi,\gamma)$ respectively, and let us start by considering the covariance
      \begin{equation}
        \Sigma^{AF}_{{\bf l}{\bf l}'}\equiv\left\langle\tilde{a}^\alpha_{\bf l}\tilde{b}^{\beta *}_{\bf l}\tilde{f}^\phi_{{\bf l}'}\tilde{g}^{\gamma *}_{{\bf l}'}\right\rangle-\left\langle\tilde{a}^\alpha_{\bf l}\tilde{b}^{\beta *}_{\bf l}\right\rangle\left\langle\tilde{f}^\phi_{{\bf l}'}\tilde{g}^{\gamma *}_{{\bf l}'}\right\rangle
      \end{equation}
      The covariance of the binned bandpowers $\tilde{\sf C}$ can then be computed as
      \begin{equation}\label{eq:cov_binned}
        {\rm Cov}\left({\rm vec}\left(\tilde{\sf C}^{ab}_q\right)_A,{\rm vec}\left(\tilde{\sf C}^{fg}_{q'}\right)_F\right)=\sum_{{\bf l}\in q} B^{\bf l}_q\sum_{{\bf l}'\in q'} B^{{\bf l}'}_{q'}\,\Sigma^{AF}_{{\bf l}{\bf l}'}.
      \end{equation}
      which can then be used to estimate the covariance of the mode-decoupled bandpowers multiplying it by the inverse mode-coupling matrix twice. I.e., schematically:
      \begin{equation}
        {\rm Cov}\left(\hat{\sf C}\right)=\mathcal{M}^{-1}\cdot{\rm Cov}\left(\tilde{C}\right)\cdot\left(\mathcal{M}^{-1}\right)^{T},
      \end{equation}
      where we have suppressed all indices for simplicity. The problem of estimating the pseudo-$C_\ell$ covariance therefore reduces to estimating $\Sigma^{AC}_{{\bf l}{\bf l}'}$.

@@

      Now, in what follows, we will be concerned with the auto- and cross-correlations of spin-0 and spin-2 fields. Thus, to simplify the notation, we will enumerate the different types of coupling coefficients that exist for a spin-0 field with a single component that we will call $\delta$, in analogy to the projected galaxy overensity, and for a spin-2 field $\boldsymbol{\gamma}$ with $E$ and $B$ components $\gamma_E$ and $\gamma_B$, in analogy to the cosmic shear field. With this setup, all the possible non-zero $W^{\alpha\beta,\alpha'\beta'}_{{\bf l}{\bf l}'}$ can be expressed in terms of the $I^{\pm s_a,\pm s_b}_{{\bf l}{\bf l}'}$ as follows:
      \begin{align}\label{eq:coeff}
        &W^{\delta\delta,\delta\delta}_{{\bf l},{\bf l}'}=I^{0,0}_{{\bf l}{\bf l}'}; \\
        &W^{\delta\gamma_E,\delta\gamma_E}_{{\bf l},{\bf l}'}=W^{\delta\gamma_B,\delta\gamma_B}_{{\bf l},{\bf l}'}=I^{0,+2}_{{\bf l},{\bf l}'};\hspace{12pt}
        W^{\delta\gamma_E,\delta\gamma_B}_{{\bf l},{\bf l}'}=-W^{\delta\gamma_B,\delta\gamma_E}_{{\bf l},{\bf l}'}=-i\,I^{0,-2}_{{\bf l},{\bf l}'};\\
        &W^{\gamma_E\gamma_E,\gamma_E\gamma_E}_{{\bf l},{\bf l}'}=W^{\gamma_E\gamma_B,\gamma_E\gamma_B}_{{\bf l},{\bf l}'}=W^{\gamma_B\gamma_E,\gamma_B\gamma_E}_{{\bf l},{\bf l}'}=W^{\gamma_B\gamma_B,\gamma_B\gamma_B}_{{\bf l},{\bf l}'}=I^{+2,+2}_{{\bf l}{\bf l}'}\\
        &W^{\gamma_E\gamma_E,\gamma_B\gamma_B}_{{\bf l},{\bf l}'}=W^{\gamma_B\gamma_B,\gamma_E\gamma_E}_{{\bf l},{\bf l}'}=-W^{\gamma_B\gamma_E,\gamma_E\gamma_B}_{{\bf l},{\bf l}'}=-W^{\gamma_E\gamma_B,\gamma_B\gamma_E}_{{\bf l},{\bf l}'}=I^{-2,-2}_{{\bf l}{\bf l}'}\\
        &W^{\gamma_E\gamma_E,\gamma_E\gamma_B}_{{\bf l},{\bf l}'}=-W^{\gamma_E\gamma_B,\gamma_E\gamma_E}_{{\bf l},{\bf l}'}=W^{\gamma_B\gamma_E,\gamma_B\gamma_B}_{{\bf l},{\bf l}'}=-W^{\gamma_B\gamma_B,\gamma_B\gamma_E}_{{\bf l},{\bf l}'}=-i\,I^{+2,-2}_{{\bf l}{\bf l}'}\\
        &W^{\gamma_E\gamma_E,\gamma_B\gamma_E}_{{\bf l},{\bf l}'}=W^{\gamma_E\gamma_B,\gamma_B\gamma_B}_{{\bf l},{\bf l}'}=-W^{\gamma_B\gamma_E,\gamma_E\gamma_E}_{{\bf l},{\bf l}'}=-W^{\gamma_B\gamma_B,\gamma_E\gamma_B}_{{\bf l},{\bf l}'}=i\,I^{-2,+2}_{{\bf l}{\bf l}'}.
      \end{align}
      Thus, in principle we only need to compute 7 different types of terms ($I^{0,0}$, $I^{0,\pm2}$, $I^{\pm2,\pm2}$ and $I^{\pm2,\mp2})$). In order to simplify these expressions further we follow \cite{2017A&A...602A..41C} and neglect all gradients of the masks, which allows us to relate the different $I^{\pm s_a,\pm s_b}$ through the following set of identities:
      \begin{align}\nonumber
        \summ{x}w({\bf x})\left(\bar{\eth}^2q({\bf l},{\bf x})\right)^*\,\bar{\eth}^2q({\bf k},{\bf x})
        &=\summ{x}w({\bf x})\eth^2 q^*({\bf l},{\bf x})\,\bar{\eth}^2q({\bf k},{\bf x})\\\nonumber
        &=\summ{x}q^*({\bf l},{\bf x})\,\eth^2\left(\bar{\eth}^2q({\bf k},{\bf x})w({\bf x})\right)\\\nonumber
        &\simeq\summ{x}q^*({\bf l},{\bf x})\,\left(\eth^2\bar{\eth}^2q({\bf k},{\bf x})\right)w({\bf x})\\
        &=\frac{1}{\beta^2_{k,2}}\summ{x}q^*({\bf l},{\bf x})\,q({\bf k},{\bf x})w({\bf x})\\\nonumber
        &=\summ{x}q^*({\bf l},{\bf x})\,\left(\bar{\eth}^2\eth^2q({\bf k},{\bf x})\right)w({\bf x})\\\nonumber
        &=\summ{x}\bar{\eth}^2\left(w({\bf x})\,q^*({\bf l},{\bf x})\right)\,\eth^2q({\bf k},{\bf x})\\
        &\simeq\summ{x}w({\bf x})\,\left(\eth^2\,q({\bf l},{\bf x})\right)^*\,\eth^2q({\bf k},{\bf x}),
      \end{align}
      where we have made repeated use of integration by parts.

>>>>

      Let $A$ and $F$ be the vector indices corresponding to the pairs of
      field indices $(\alpha,\beta)$ and $(\phi,\gamma)$, respectively, and let us start by considering the covariance
      \begin{equation}
        \Sigma^{AF}_{{\bf l}{\bf l}'}\equiv\left\langle\tilde{a}^\alpha_{\bf l}\tilde{b}^{\beta *}_{\bf l}\tilde{f}^\phi_{{\bf l}'}\tilde{g}^{\gamma *}_{{\bf l}'}\right\rangle-\left\langle\tilde{a}^\alpha_{\bf l}\tilde{b}^{\beta *}_{\bf l}\right\rangle\left\langle\tilde{f}^\phi_{{\bf l}'}\tilde{g}^{\gamma *}_{{\bf l}'}\right\rangle
      \end{equation}
      The covariance of the binned bandpowers $\tilde{\sf C}$ can then be computed as
      \begin{equation}\label{eq:cov_binned}
        {\rm Cov}\left({\rm vec}\left(\tilde{\sf C}^{ab}_q\right)_A,{\rm vec}\left(\tilde{\sf C}^{fg}_{q'}\right)_F\right)=\sum_{{\bf l}\in q} B^{\bf l}_q\sum_{{\bf l}'\in q'} B^{{\bf l}'}_{q'}\,\Sigma^{AF}_{{\bf l}{\bf l}'}.
      \end{equation}
      which can then be used to estimate the covariance of the mode-decoupled bandpowers multiplying it by the inverse mode-coupling matrix twice. I.e., schematically:
      \begin{equation}
        {\rm Cov}\left(\hat{\sf C}\right)=\mathcal{M}^{-1}\cdot{\rm Cov}\left(\tilde{C}\right)\cdot\left(\mathcal{M}^{-1}\right)^{T},
      \end{equation}
      where we have suppressed all indices for simplicity. The problem of estimating the pseudo-$C_\ell$ covariance therefore reduces to estimating $\Sigma^{AC}_{{\bf l}{\bf l}'}$.

@@

      Now, in what follows, we will be concerned with the auto- and
      cross-correlations of spin-0 and spin-2 fields. Thus, to simplify the
      notation, we will enumerate the different types of coupling coefficients
      that exist for a spin-0 field with a single component that we will call
      $\delta$, in analogy to the projected galaxy overensity, and for a
      spin-2 field, $\boldsymbol{\gamma}$, with $E$ and $B$ components, $\gamma_E$ and $\gamma_B$, in analogy to the cosmic shear field. With this setup, all the possible non-zero $W^{\alpha\beta,\alpha'\beta'}_{{\bf l}{\bf l}'}$ can be expressed in terms of the $I^{\pm s_a,\pm s_b}_{{\bf l}{\bf l}'}$ as follows:
      \begin{align}\label{eq:coeff}
        &W^{\delta\delta,\delta\delta}_{{\bf l},{\bf l}'}=I^{0,0}_{{\bf l}{\bf l}'}; \\
        &W^{\delta\gamma_E,\delta\gamma_E}_{{\bf l},{\bf l}'}=W^{\delta\gamma_B,\delta\gamma_B}_{{\bf l},{\bf l}'}=I^{0,+2}_{{\bf l},{\bf l}'};\hspace{12pt}
        W^{\delta\gamma_E,\delta\gamma_B}_{{\bf l},{\bf l}'}=-W^{\delta\gamma_B,\delta\gamma_E}_{{\bf l},{\bf l}'}=-i\,I^{0,-2}_{{\bf l},{\bf l}'};\\
        &W^{\gamma_E\gamma_E,\gamma_E\gamma_E}_{{\bf l},{\bf l}'}=W^{\gamma_E\gamma_B,\gamma_E\gamma_B}_{{\bf l},{\bf l}'}=W^{\gamma_B\gamma_E,\gamma_B\gamma_E}_{{\bf l},{\bf l}'}=W^{\gamma_B\gamma_B,\gamma_B\gamma_B}_{{\bf l},{\bf l}'}=I^{+2,+2}_{{\bf l}{\bf l}'}\\
        &W^{\gamma_E\gamma_E,\gamma_B\gamma_B}_{{\bf l},{\bf l}'}=W^{\gamma_B\gamma_B,\gamma_E\gamma_E}_{{\bf l},{\bf l}'}=-W^{\gamma_B\gamma_E,\gamma_E\gamma_B}_{{\bf l},{\bf l}'}=-W^{\gamma_E\gamma_B,\gamma_B\gamma_E}_{{\bf l},{\bf l}'}=I^{-2,-2}_{{\bf l}{\bf l}'}\\
        &W^{\gamma_E\gamma_E,\gamma_E\gamma_B}_{{\bf l},{\bf l}'}=-W^{\gamma_E\gamma_B,\gamma_E\gamma_E}_{{\bf l},{\bf l}'}=W^{\gamma_B\gamma_E,\gamma_B\gamma_B}_{{\bf l},{\bf l}'}=-W^{\gamma_B\gamma_B,\gamma_B\gamma_E}_{{\bf l},{\bf l}'}=-i\,I^{+2,-2}_{{\bf l}{\bf l}'}\\
        &W^{\gamma_E\gamma_E,\gamma_B\gamma_E}_{{\bf l},{\bf l}'}=W^{\gamma_E\gamma_B,\gamma_B\gamma_B}_{{\bf l},{\bf l}'}=-W^{\gamma_B\gamma_E,\gamma_E\gamma_E}_{{\bf l},{\bf l}'}=-W^{\gamma_B\gamma_B,\gamma_E\gamma_B}_{{\bf l},{\bf l}'}=i\,I^{-2,+2}_{{\bf l}{\bf l}'}.
      \end{align}
      Thus, in principle, we only need to compute 7 different types of terms
      ($I^{0,0}$, $I^{0,\pm2}$, $I^{\pm2,\pm2}$ and $I^{\pm2,\mp2})$). In
      order to simplify these expressions further, we follow \cite{2017A&A...602A..41C} and neglect all gradients of the masks, which allows us to relate the different $I^{\pm s_a,\pm s_b}$ through the following set of identities:
      \begin{align}\nonumber
        \summ{x}w({\bf x})\left(\bar{\eth}^2q({\bf l},{\bf x})\right)^*\,\bar{\eth}^2q({\bf k},{\bf x})
        &=\summ{x}w({\bf x})\eth^2 q^*({\bf l},{\bf x})\,\bar{\eth}^2q({\bf k},{\bf x})\\\nonumber
        &=\summ{x}q^*({\bf l},{\bf x})\,\eth^2\left(\bar{\eth}^2q({\bf k},{\bf x})w({\bf x})\right)\\\nonumber
        &\simeq\summ{x}q^*({\bf l},{\bf x})\,\left(\eth^2\bar{\eth}^2q({\bf k},{\bf x})\right)w({\bf x})\\
        &=\frac{1}{\beta^2_{k,2}}\summ{x}q^*({\bf l},{\bf x})\,q({\bf k},{\bf x})w({\bf x})\\\nonumber
        &=\summ{x}q^*({\bf l},{\bf x})\,\left(\bar{\eth}^2\eth^2q({\bf k},{\bf x})\right)w({\bf x})\\\nonumber
        &=\summ{x}\bar{\eth}^2\left(w({\bf x})\,q^*({\bf l},{\bf x})\right)\,\eth^2q({\bf k},{\bf x})\\
        &\simeq\summ{x}w({\bf x})\,\left(\eth^2\,q({\bf l},{\bf x})\right)^*\,\eth^2q({\bf k},{\bf x}),
      \end{align}
      where we have made repeated use of integration by parts.
